---
title: "Week2DataViz"
subtitle: "AlistairGJ"
output:
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Andy Kirk does NOT include 'strive for form over function' ANS 'Strive for form and function'
- Health star rating ORDINAL
-- Order to it - this is the main determining factor in how healthy something is

- Kaiser Fung's trifecta check-up does NOT include the sample size (this falls under what does the data say)

Picking between figure and background

- GGPLOT2 - Hadley Wickham 
& 'The Grammar of Graphics'
-- Data Viz, layered approach
-- Can very quickly add layers to create viz that we want!
-- Learn theory and how to code
-- 

```{r block1, echo=FALSE}
library(ggplot2)
```

#### Check GGPLOT website
#### Buy GGPLOT book

i. Data -> data
ii. Geometric Objects -> geoms (aesthetics - the 'small bits and pieces')
-- Points, lines, colour scales e.t.c.,
iii. Statistical Transformations -> stats (are we vizualising the data or a statistical transformation of the data?)
iv. Scales -> scale (breaking aesthetic up to tell us about a variable...)
v. 
vi. 

-- Facet with a categorical variable

You can also embed plots, for example:

```{r block2, eval=TRUE}
Cars <- read.csv('cars.csv')
```













