---
title: "Week2DataViz"
subtitle: "AlistairGJ"
output:
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Andy Kirk does NOT include 'strive for form over function' ANS 'Strive for form and function'
- Health star rating ORDINAL
-- Order to it - this is the main determining factor in how healthy something is

- Kaiser Fung's trifecta check-up does NOT include the sample size (this falls under what does the data say)

Picking between figure and background

- GGPLOT2 - Hadley Wickham 
& 'The Grammar of Graphics'
-- Data Viz, layered approach
-- Can very quickly add layers to create viz that we want!
-- Learn theory and how to code
-- 

```{r block1, echo=FALSE}
library(ggplot2)
library(magrittr)
library(dplyr)
```

#### Check GGPLOT website
#### Buy GGPLOT book

i. Data -> data
ii. Geometric Objects -> geoms (aesthetics - the 'small bits and pieces')
-- Points, lines, colour scales e.t.c.,
iii. Statistical Transformations -> stats (are we vizualising the data or a statistical transformation of the data?)
iv. Scales -> scale (breaking aesthetic up to tell us about a variable...)
v. 
vi. 

-- Facet with a categorical variable

You can also embed plots, for example:

```{r block2, eval=TRUE}
Cars <- read.csv('cars.csv')
```

### Qplot
- A good 'go to' function


```{r block3, eval=TRUE}
Cars$Sports <- Cars$Sports %>% factor(levels=c(0,1), 
                                      labels=c('No','Yes'), ordered=TRUE)

Cars$Sport_utility <- Cars$Sport_utility %>% factor(levels=c(0,1), 
                                                    labels=c('No','Yes'), ordered=TRUE)

Cars$Wagon <- Cars$Wagon %>% factor(levels=c(0,1), 
                                    labels=c('No','Yes'), ordered=TRUE)

Cars$Minivan <- Cars$Minivan %>% factor(levels=c(0,1), 
                                        labels=c('No','Yes'), ordered=TRUE)

Cars$Pickup <- Cars$Pickup %>% factor(levels=c(0,1),
                                      labels=c('No','Yes'), ordered=TRUE)

Cars$All_wheel_drive <- Cars$All_wheel_drive %>% factor(levels=c(0,1), 
                                                        labels=c('No','Yes'), ordered=TRUE)

Cars$Rear_wheel_drive <- Cars$Rear_wheel_drive %>% factor(levels=c(0,1), 
                                                          labels=c('No','Yes'), ordered=TRUE)

Cars$Cylinders <- Cars$Cylinders %>% as.factor()
```


```{r block4, eval=TRUE}
qplot(x = Cylinders, y = Kilowatts, data = Cars, geom = "boxplot")
```

```{r block5, eval=TRUE}
Alcohol <- read.csv('Student_alcohol_survey.csv')
```

```{r block6, eval=TRUE}
p1 <- ggplot(data = Alcohol, mapping = aes(x = as.factor(Dalc), y = G3))
p1 + geom_boxplot()

https://archive.ics.uci.edu/ml/machine-learning-databases/abalone/abalone.data 



```







