---
title: "Week2DataViz"
subtitle: "AlistairGJ"
output:
  html_notebook: default
---

## Group/Individual Details

* Alistair Grevis-James (s3644119)

## Executive Statement

In your own words, provide a brief summary of the investigation. Explain the aim of the investigation, the procedure, sample, variables, main findings and conclusions. Write this section last after you have performed hypothesis testing. (Word count Max: 300 words)

### Introduction & Hypothesis


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the Libraries

```{r importingLibraries}
library(ggplot2)
library(magrittr)
library(dplyr)
library(readr)
library(rvest)
```

## 

```{r, echo=FALSE}
census <- read_csv("table.csv", skip = 10)
```

```{r, echo=FALSE}
head(census)
```

* Checking the size
```{r}
dim(census)
```

* Check first column (nomenclature?)
```{r}
c(census[1:21,1])
```


```{r, echo=FALSE}
row1 <- census[,1:25]
print(row1)
```



```{r}
census2 <- read.csv("table.csv", sep=";")
# Gives one column of 405 obs, where each ob is separated by commas
```





```{r}
census <- read.table("table.csv", sep=",", header = TRUE, stringsAsFactors = FALSE)
```


http://abs.gov.au/
1. Census data
2. Table Builder
3. Open TableBuilder Guest
4. 2016 Census - Employment, Income and Education (open table)
5. Download Table as CSV
6. File 'table.csv' added to working directory























```{r, echo=FALSE}
census <- read_csv("table2.csv", sep=",")
```

```{r}
#census2 <- read.csv("table2.csv", sep=";")
# Gives one column of 405 obs, where each ob is separated by commas
```





```{r}
census <- read.table("table2.csv", sep=",", header = TRUE)
```














